\documentclass[11pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{parskip}

% Page layout
\geometry{
    left=1in,
    right=1in,
    top=1in,
    bottom=1in
}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

% Sender information
\address{
    Avijit Das \\
    Boulder, CO \\
    +1-858-519-6587 \\
    \href{mailto:avijitnsec@gmail.com}{avijitnsec@gmail.com} \\
    \href{https://linkedin.com/in/avijitnsec}{linkedin.com/in/avijitnsec}
}

\signature{Avijit Das}

\begin{document}

% Recipient information - customize this section for each application
\begin{letter}{
    Hiring Manager \\
    [Company Name] \\
    [Company Address] \\
    [City, State ZIP]
}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Principal/Senior Software Engineer position at [Company Name]. With over 16 years of specialized expertise in medical device software development, embedded systems, and platform security, I am confident that my technical leadership and proven track record of delivering life-critical solutions align perfectly with your organization's needs.

Currently serving as Principal Software Engineer at Medtronic, I lead the development of life-critical endotracheal intubation medical devices, where I architect respiratory algorithms and safety features in C++ that directly impact patient outcomes. My work encompasses the full spectrum of medical device software development—from real-time patient monitoring systems with sub-second latency requirements to secure connectivity solutions enabling remote ventilator access and over-the-air updates, all while maintaining strict FDA regulatory compliance and medical device security standards.

My technical expertise spans multiple critical domains:

\textbf{Medical Device Software Excellence:} I have architected end-to-end solutions for ICU ventilator systems, implementing advanced breathing technology algorithms and intuitive GUI frameworks that balance complex clinical data presentation with operational simplicity under high-stress conditions. My debugging tools have reduced integration defects by 35\%, directly improving patient safety and accelerating time-to-market.

\textbf{Security and Platform Engineering:} During my tenure at Qualcomm, I led SELinux/SEAndroid enablement on Snapdragon platforms, designing comprehensive security policies that enhanced the security posture across millions of OEM device deployments. I achieved a 20\% boot time optimization while maintaining rigorous security standards—demonstrating my ability to balance performance with safety-critical requirements.

\textbf{System-Level Expertise:} My deep knowledge of Linux kernel development, Android framework optimization, and embedded systems architecture enables me to solve complex technical challenges across the full stack. From porting Trinity Linux system call fuzzer for vulnerability detection to implementing kmemleak support for systematic memory leak tracking, I bring comprehensive debugging and optimization capabilities.

\textbf{Cross-Functional Leadership:} I excel at collaborating with diverse stakeholders—from healthcare professionals and regulatory bodies to OEM partners and open-source communities. My experience managing enterprise-scale codebases, establishing code review workflows, and providing expert technical support has consistently enabled on-schedule product releases and successful regulatory approvals.

What distinguishes my approach is the combination of technical depth with practical impact. Whether optimizing Android ICS memory management to enable deployment on resource-constrained devices or creating packet tracking tools that accelerate quality assurance processes, I focus on delivering solutions that drive measurable business outcomes while maintaining the highest standards of quality and safety.

I am particularly drawn to [Company Name] because of [specific reason related to company's mission, products, or technology]. I am excited about the opportunity to bring my expertise in [relevant technical area] to contribute to [specific project or goal].

I would welcome the opportunity to discuss how my experience in medical device software development, security engineering, and technical leadership can contribute to [Company Name]'s continued success. Thank you for considering my application. I look forward to speaking with you soon.

\closing{Sincerely,}

\end{letter}

\end{document}
